\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[top=0.5in, bottom=0.5in, left=0.65in, right=0.65in]{geometry}

\usepackage{tgheros}
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parskip}{0pt}

\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{7pt}{4pt}

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1\vspace{0.5pt}}}

\setlist[itemize,1]{leftmargin=0pt, label={}, itemsep=2pt, topsep=3pt, parsep=0pt}
\setlist[itemize,2]{leftmargin=14pt, label=\textbullet, itemsep=1.5pt, topsep=2pt, parsep=0pt}

\begin{document}

%-------------------- HEADER --------------------
\begin{center}
  {\huge \scshape Yug Upadhyay} \\ \vspace{3pt}
  \textit{Full-Stack Product Engineer (AI-Augmented Development)} \\ \vspace{4pt}
  \small
  \href{mailto:yugyugupadhyay@gmail.com}{yugyugupadhyay@gmail.com} $|$
  +91 9081084555 $|$
  \href{https://github.com/Yug1921}{github.com/Yug1921} $|$
  \href{https://linkedin.com/in/yug-upadhyay}{linkedin.com/in/yug-upadhyay} $|$
  Ahmedabad, Gujarat, India
\end{center}

\vspace{1pt}

%-------------------- SUMMARY --------------------
\section*{ Summary}
\vspace{2pt}
\small Full-Stack Developer with hands-on experience building production-grade web applications using React.js, Node.js, and AWS. Proven ability to optimize system performance (60s $\rightarrow$ 3s) and deliver responsive, scalable UI/UX. Seeking a software engineering role to contribute to real-world product development and grow within a collaborative engineering team.

%-------------------- SKILLS --------------------
\section*{Technical Skills}
\begin{itemize}
  \resumeItem{\textbf{Languages:} JavaScript (ES6+), Python, Java, C/C++, TypeScript, R}
  \resumeItem{\textbf{Frontend:} React.js, Next.js, Redux, HTML5, CSS3, TailwindCSS, ShadCN UI}
  \resumeItem{\textbf{Backend:} Node.js, Express.js, REST API Design, JWT Authentication}
  \resumeItem{\textbf{Databases:} MySQL, MongoDB, Firebase (Firestore)}
  \resumeItem{\textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda, CloudWatch, IAM, VPC), CI/CD basics, Cloud Security}
  \resumeItem{\textbf{Developer Tools:} Git, GitHub, Postman, Figma, Tableau, Power BI}
  \resumeItem{\textbf{Concepts:} Data Structures \& Algorithms, OOP (Java), Agile/Scrum, Cloud Security Fundamentals}
\end{itemize}

%-------------------- EXPERIENCE --------------------
\section*{Professional Experience}
\begin{itemize}
  \item
  \textbf{Software Developer Intern --- Sparks to Ideas} \hfill \textbf{2023}
  \begin{itemize}
    \item Developed and maintained production React components, improving UI consistency and user experience across the platform.
    \item Optimized React state management and custom Hooks, reducing unnecessary re-renders and improving performance for large data payloads.
    \item Built reusable, well-documented component libraries and collaborated in Agile sprints including code reviews and daily stand-ups.
    \item Worked closely with senior engineers to deliver features on schedule, gaining exposure to end-to-end software development workflows.
  \end{itemize}
\end{itemize}

%-------------------- PROJECTS --------------------
\section*{Projects}
\begin{itemize}

  \item
  \textbf{DPI --- Deep Packet Inspector} \hfill \textbf{2025} \\
  \textit{Java $\cdot$ Node.js $\cdot$ Express.js $\cdot$ React.js $\cdot$ TailwindCSS $\cdot$ Multithreading}
  \begin{itemize}
    \item Engineered an end-to-end DPI system to process PCAP files, classify network traffic by application or domain, and generate filtered PCAP outputs for cybersecurity and network monitoring use cases.
    \item Achieved 95\%+ performance improvement, reducing processing time from $\sim$60s to 1--3s via optimized multi-threaded worker shutdown, improved concurrency, and max-packet controls.
    \item Implemented concurrent flow and application statistics reporting covering active flows, app distribution, thread-level processing stats, and detected domains and SNI signals.
    \item Developed a React.js dashboard with persistent state management and downloadable analysis artifacts, enabling reliable demo and reporting workflows.
  \end{itemize}

  \item
  \textbf{RMS --- Restaurant Management System} \hfill \textbf{2024} \\
  \textit{React.js $\cdot$ Node.js $\cdot$ Express.js $\cdot$ MySQL}
  \begin{itemize}
    \item Built a full-stack restaurant management platform handling reservations, order tracking, and table bookings with secure, persistent data storage.
    \item Designed a fully responsive UI using React.js and Bootstrap; implemented RESTful APIs with Express.js for all CRUD operations.
    \item Applied a normalized MySQL database schema to ensure data integrity and efficient query performance under concurrent operations.
  \end{itemize}

\end{itemize}

%-------------------- EDUCATION --------------------
\section*{Education}
\begin{itemize}

  \item
  \textbf{B.Tech in Computer Science Engineering --- Karnavati University} \hfill \textit{2022 -- Present} \\
  \small Ahmedabad, Gujarat

  \item
  \textbf{Diploma in Information Technology --- LJ University} \hfill \textit{2019 -- 2022} \\
  \small CGPA: 7.50 / 10

  \item
  \textbf{Secondary Education (SSC) --- Nelson's High School} \hfill \textit{2019} \\
  \small Score: 85.11\%

\end{itemize}

%-------------------- CERTIFICATIONS --------------------
\section*{Certifications}
\begin{itemize}
  \resumeItem{AWS Academy Graduate --- Cloud Security Foundations \hfill 2026}
\end{itemize}

\end{document}  